---
title: "p8105_hw2_KAB2310"
author: "Kamiah Brown"
date: "2024-10-01"
output: github_document
---
## This is my submission for Homework 5.

# Set up 
```{r}
library(tidyverse)
library(dplyr)
library(readxl)
library(broom)
```

# Question 1
# Function 
```{r}
shared_birthday = function(n) {
  birthdays = sample(1:365, n, replace = TRUE)
  return(any(duplicated(birthdays)))
}
```

# Running function 1000 times for each group size between 2 and 50
```{r}
group_sizes = 2:50
simulations = 10000

results = 
  tibble(group_size = group_sizes) |>
  mutate(
    output_lists = map(group_size, ~rerun(simulations, shared_birthday(.x))),
    estimate_df = map(output_lists, ~tibble(shared_birthday = unlist(.)))
     ) |>
  select(-output_lists) |>
  unnest(estimate_df) |>
  group_by(group_size) |>
  summarize(probability = mean(shared_birthday), .groups = 'drop')

results
```

# Probability as a function (Shared Birthday) of group size
```{r}
results |>
  ggplot(aes(x = group_size, y = probability)) +
  geom_line() +
  geom_point() +
  labs(title = "Probability of Shared Birthday vs Group Size",
       x = "Group Size",
       y = "Probability of Shared Birthday") +
  theme_minimal()
```

#Comments
The plot demonstrates that as the group size increases, the probability of at least two people sharing a birthday rises quickly at first and then levels off as it approaches 1, highlighting a nonlinear relationship. While smaller groups show a rapid increase in the likelihood of shared birthdays, the rate of increases slows signficantly for larger group sizes (beyond 30), where the probability is approaching 1.

# Question 2 
```{r}
n = 30
sigma = 5

sim_power = function(mu){
  
  tibble(
    x = rnorm(n, mu, sigma)) |> 
      summarize(
        tidy(t.test(x, mu = 0, conf.level = 0.95))) |> 
    select(estimate, p.value)
  
}

# Generate 5000 datasets from the model
sim_result = expand_grid(
  mu = 0:6,
  iter = 1:5000) |> 
  mutate(samp_res = map(mu, sim_power)) |> 
  unnest(samp_res)

```
# plot showing the proportion of times the null was rejected 
```{r}
sim_result |> 
  group_by(mu) |> 
  summarize(
    power = mean(p.value < 0.05)
  ) |> 
  ggplot(aes(x = mu, y = power)) +
  geom_point() +
  geom_line()
```

# plot showing the average estimate of mu 
```{r}

```

#Comments 




